Matching bullets

### 2015-11-23 imaging-paper.Rnw
got to match the striation_identify with the rest again

lines <- matches %>% group_by(lineid) %>% summarise(
  meany = mean(y, na.rm=T),
  miny = min(y, na.rm=T),
  maxy = max(y, na.rm=T) + 1.5625,
  match = isMatch(lineid, type),
  type = type1[1]
)

@
\begin{figure}
\centering
    \subfloat[Crosscuts at $x = 100$.\label{fig:crosscut}]{%
<<crosscuts, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lof, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer("", palette="Set1") + theme_bw() +
  theme(legend.position = c(.9, .2))
@
    }
    \hfill
    \subfloat[Adjusted (Bullet 1-5 horizontally shifted) crosscuts at $x = 100$.\label{fig:crosscutX}]{%
<<crosscutsX, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lofX, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer(palette="Set1") + theme_bw() +
  theme(legend.position="none")
@
    }
\caption{\label{fig:cross100} Lines showing surface crosscuts at $x = 100$. A horizontal shift of the values of Bullet 1-5 to the right shows the similarity of the striation marks.}
\end{figure}

>>>>

lines <- matches %>% group_by(lineid) %>% summarise(
  meany = mean(y, na.rm=T),
  miny = min(y, na.rm=T),
  maxy = max(y, na.rm=T) + 1.5625,
  match = isMatch(lineid, type),
  type = type1[1]
)
lines <- subset(lines, lineid != 0)
@
\begin{figure}
\centering
    \subfloat[Crosscuts at $x = 100$.\label{fig:crosscut}]{%
<<crosscuts, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lof, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer("", palette="Set1") + theme_bw() +
  theme(legend.position = c(.9, .2))
@
    }
    \hfill
    \subfloat[Adjusted (Bullet 1-5 horizontally shifted) crosscuts at $x = 100$.\label{fig:crosscutX}]{%
<<crosscutsX, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lofX, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer(palette="Set1") + theme_bw() +
  theme(legend.position="none")
@
    }
\caption{\label{fig:cross100} Lines showing surface crosscuts at $x = 100$. A horizontal shift of the values of Bullet 1-5 to the right shows the similarity of the striation marks.}
\end{figure}
